---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# UtilsDataRSV

<!-- badges: start -->
<!-- badges: end -->

The goal of UtilsDataRSV is to make miscellaneous data processing tasks easier. 

## Installation

You can install UtilsDataRSV from [GitHub](https://www.github.com) with:

```{r , eval = FALSE}
if(!require("remotes", quietly = TRUE)) install.packages('remotes')
remotes::install_github("MiguelRodo/UtilsDataRSV.git")
```

## Examples

Load the package. 
```{r }
library(UtilsDataRSV)
```

Display a random selection of (a limited number) of unique entries from each column. 
```{r view_cols}
data('mtcars')
view_cols(mtcars)
```

Correct error where Excel reads in incorrectly due to differences in the decimal symbol between systems. At present only fixes error where original data uses a comma and system being read into uses a full stop. 
```{r convert_character_to_number_correctly}
# vector of data (as if from Excel)
x <- c("1,32", "1", "0,23", "3,23E-2", NA)
x_corrected <- convert_character_to_number_correctly(x = x)
# original data alongside corrected data
tibble::tibble(original = x, corrected = x_corrected)
```

Display a subset of entries per group (a thin wrapper around `dplyr::group_by` and `dplyr::slice`).
```{r view_slice}
data('cars')
cars[,'grp'] <- rep(letters[1:5], each = 10)
view_slice(cars, group = 'grp', n_slice = 2)
```
